---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

# rappalyzer

Identify Technologies Used On Websites

**WIP** - basic tech stack identification is complete and some version info seems to be working but I think there's an isssue with the regexes & compatibility with `ore`.

## Description

The 'Wappalyzer' project <https://wappalyzer.com/> maintains a database
of features that can be compared and combined to identify what technologies -- servers,
frameworks, analytics tools, etc. -- are being used by a target web site. Methods are
provided that mimic the functionality of 'Wappalyzer' in R.

## Contents

The following functions are implemented:

- `rappalyze`:	Identify technologies used on a given site/URL
- `rapp_icon`:	Provide the full path to the "icon" file within the package
- `rebuild_apps_inventory`:	Rebuild apps inventory with a different master file

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/rappalyzer")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rappalyzer)
library(tidyverse)

# current verison
packageVersion("rappalyzer")

rappalyze("https://rud.is/b") %>% unnest()

rappalyze("https://blog.rapid7.com")

rappalyze("https://community.rstudio.com") %>% unnest()

rappalyze("https://www.quantcast.com")

rappalyze("https://jquery.com/") %>% unnest()

rappalyze("https://wappalyzer.com")
```

